02_DESeq_characterization

### 2019-12-02 analysis/03_DESeq2_characterization.Rmd
now with manip volcanos

```{r plotDEGs}
plot.volcano <- function(data, whichfactor, up, down, mycolors){

  volcano <- data %>%
    ggplot(aes(x = lfc, y = logpadj)) + 
    geom_point(aes(color = direction, shape = tissue), size = 2, 
               alpha = 0.75, na.rm = T) + 
    theme_minimal() +
    scale_color_manual(values = mycolors,
                       name = " ",
                       drop = FALSE) +
    ylim(c(0,30)) +  
    xlim(c(-8,8)) +
    labs(y = "-log10(p)", x = " ")  +
    theme(legend.position = "none",
          legend.direction = "horizontal",
          legend.spacing.x = unit(-0.1, 'cm'),
          legend.margin=margin(t=-0.25, r=0, b=0, l=0, unit="cm"),
          panel.grid = element_blank()) +
    scale_shape_manual(values = myshapes)
  return(volcano)
}

a <- plot.volcano(control.bldg, "treatment", "bldg", "control", colorsvolcano)
b <- plot.volcano(bldg.lay, "treatment", "lay", "bldg", colorsvolcano)
c <- plot.volcano(lay.inc.d3, "treatment", "inc.d3", "lay", colorsvolcano) 
d <- plot.volcano(inc.d3.inc.d9, "treatment", "inc.d9", "inc.d3", colorsvolcano) 
e <- plot.volcano(inc.d9.inc.d17, "treatment", "inc.d17", "inc.d9", colorsvolcano)
f <- plot.volcano(inc.d17.hatch, "treatment", "hatch", "inc.d17", colorsvolcano) 
g <- plot.volcano(hatch.n5, "treatment", "n5", "hatch", colorsvolcano) 
h <- plot.volcano(n5.n9, "treatment", "n9", "n5", colorsvolcano)

@@

## males and females

>>>>

```{r plotDEGs}
a <- plot.volcano(control.bldg, "treatment", "bldg", "control", colorsvolcano)
b <- plot.volcano(bldg.lay, "treatment", "lay", "bldg", colorsvolcano)
c <- plot.volcano(lay.inc.d3, "treatment", "inc.d3", "lay", colorsvolcano) 
d <- plot.volcano(inc.d3.inc.d9, "treatment", "inc.d9", "inc.d3", colorsvolcano) 
e <- plot.volcano(inc.d9.inc.d17, "treatment", "inc.d17", "inc.d9", colorsvolcano)
f <- plot.volcano(inc.d17.hatch, "treatment", "hatch", "inc.d17", colorsvolcano) 
g <- plot.volcano(hatch.n5, "treatment", "n5", "hatch", colorsvolcano) 
h <- plot.volcano(n5.n9, "treatment", "n9", "n5", colorsvolcano)

@@

## males
